Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-20 Scripts/Initial_Analysis.Rmd
Ran sensitivity for alternative method

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    # Alternative method sensitivity analysis
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    # group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

    taxon <- unique(Raw_Result$taxon_key)
    name_raw <- paste(my_path("R",extra_path = "/Emergence_last_raw_p90/"),taxon,"_emergence_raw.csv",sep="")

@@

    name <- paste(my_path("R",extra_path = "/Emergence_last_p90/"),taxon_key,"_emergence.txt",sep="")

@@

# Already modeled species
spp_done <- list.files(my_path("R", extra_path = "Emergence"))

@@

rand_plot <- sample(spp_reman,5)

@@

    Emerging_result <- bind_rows(
      mclapply(spp_list,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Abd",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid,
               p = 0.90,
               Plot = F
      )
    )

>>>>

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    # Alternative method sensitivity analysis
    group_by(taxon_key,neighbour_id,year) %>% #Average historic data per year first
    # group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

    taxon <- unique(Raw_Result$taxon_key)
    name_raw <- paste(my_path("R",extra_path = "/Emergence_alt_sens_raw/"),taxon,"_emergence_raw.csv",sep="")

@@

    name <- paste(my_path("R",extra_path = "/Emergence_alt_sens/"),taxon_key,"_emergence.txt",sep="")

@@

# Already modeled species
spp_done <- list.files(my_path("R", extra_path = "Emergence_alt_sens"))

@@

# For plotting test
rand_plot <- sample(spp_reman,5)

# For alternative method
alt_sens <- sample(spp_reman,30)

@@

    Emerging_result <- bind_rows(
      mclapply(alt_sens,
               GetTransIndex,
               year = year_df$year,
               Hist_y = Historic_year,
               data_type = "Abd",
               ensemble_list = ensemble_list,
               Neighbours = Neighbours,
               eez_centroid = eez_centroid,
               p = 0.95, # main is 95
               Plot = F
      )
    )
